Oral contraceptives

### 2021-01-10 r_notebooks/exploring_oral_contraceptives.Rmd
Added LPA analysis

@@

@@

```{r}
source("../r_scripts/functions/mplus_plotting.R")
mplus.view.plots("../mplus_analyses/oc_gp/oac_discrep_3_class_bayes.gh5")
mplus.plot.estimated_means("../mplus_analyses/oc_gp/oac_discrep_3_class_bayes.gh5")
```

>>>>

* 2941.64 seconds 2021-01-08

@@

```{r}
library(tidyLPA)

gp_lpa_fit <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
    select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  estimate_profiles(1:8, models = c(1:3, 6)
                    #variances = c("equal", "varying"),
                    #covariances = c("zero", "varying")
                    )

gp_lpa_fit %>% 
  compare_solutions(statistics = c("AIC", "BIC"))

gp_lpa_fit %>% 
  compare_solutions(statistics = c("AIC", "BIC")) %>% 
  .[[1]] %>% 
  ggplot(aes(x = Classes, y = BIC, group = Model, colour = as.factor(Model))) +
  geom_line()

gp_lpa_fit %>%
  plot_profiles(x = ., rawdata = FALSE)
```

@@

```{r, eval=FALSE}
source("../r_scripts/functions/mplus_plotting.R")
mplus.view.plots("../mplus_analyses/oc_gp/oc_discrep_2_class_ml.gh5")
mplus.plot.estimated_means("../mplus_analyses/oc_gp/oc_discrep_2_class_ml.gh5")
mplus_models <- MplusAutomation::readModels("../mplus_analyses/oc_gp")

mplus_models$oc_discrep_1_class_bayes.out$summaries$BIC

mplus_model_summaries <- 
  MplusAutomation::readModels("../mplus_analyses/oc_gp", what = "summaries", quiet = TRUE)

mplus_model_summaries$oc_discrep_1_class_bayes.out$summaries %>% 
  squash() %>% 
  as_tibble()

length(mplus_model_summaries)
map_dfr(.x = 1:length(mplus_model_summaries), 
        .f = ~mplus_model_summaries[[.x]]$summaries$BIC)
```
